A pandemic-scale Ancestral Recombination Graph for SARS-CoV-2

### 2025-09-25 latex/main.tex
Updates from Overleaf

\subsubsection{XBE}
WIP

>>>>

\subsubsection{XBE}
https://github.com/jeromekelleher/sc2ts-paper/issues/351

In the Pango designation issue
(https://github.com/cov-lineages/pango-designation/issues/1246),
XBE was suggested as a recombinant between
BA.5.2 (left parent; most of the genome) and
BE.4 (right parent; somewhere from 23609 onwards).
However, sc2ts treats the 65 XBE samples
as non-recombinant descendants of BA.5.2
because the number of supporting sites fell
below our threshold of detection.
We have included the BE.4 lineage on the subgraph,
revealing three mutations (G22599C, C27800T, and G28681T)
which occur in parallel above the root of the XBE clade and
along the path ascending from the BE.4 sample,
suggesting that if we used k=3 as the recombinant threshold,
sc2ts would indeed detect XBE as a recombinant.
